PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-04-21 peace/papers/NAR_web_server_2009/paper.tex
Modifications to paper abstract

\begin{abstract}
  \mc{We present \peace, a stand alone tool for high-throughput {\it
      ab initio} clustering of transcript fragment sequences produced
    by Next Generation or Sanger Sequencing technologies.  It is
    freely available from
    \href{http://www.peace-tools.org}{www.peace-tools.org}.  Installed
    and managed through a download-able user-friendly GUI, \peace\/
    can process large data sets of transcript fragments of length 50
    bases or greater, grouping the fragments by gene associations with
    a sensitivity compatible to leading clustering tools.  Once
    clustered, the user can employ the GUI's analysis functions,
    facilitating easy collection of statistics and allowing them to
    single out specific clusters for more comprehensive study or
    assembly.  Using a novel minimum spanning tree based clustering
    method, \peace\/ is the equal of other leading tools in the
    literature in quality and interface.  It produces results of
    quality virtually identical to those of the \wcd\/ tool when
    applied to Sanger sequences, significantly improved results over
    \wcd\/ when applied the products of Next Generation Sequencing
    Technology, and significantly improved results over \capthree\/ in
    both cases.  In short, \peace\/ provides an intuitive graphical
    user interface and a feature-rich, parallel clustering engine that
    proves to be a valuable addition to the leading cDNA clustering
    tools.}

>>>>

\begin{abstract}
  \mc{We present \peace, a stand alone tool for high-throughput {\it
      ab initio} clustering of transcript fragment sequences produced
    by Next Generation or Sanger Sequencing technologies.  It is
    freely available from
    \href{http://www.peace-tools.org}{www.peace-tools.org}.  Installed
    and managed through a download-able user-friendly GUI, \peace\/
    can process large data sets of transcript fragments of length 50
    bases or greater, grouping the fragments by gene associations with
    a sensitivity compatible to leading clustering tools.  Once
    clustered, the user can employ the GUI's analysis functions,
    facilitating the easy collection of statistics and allowing them
    to single out specific clusters for more comprehensive study or
    assembly.  Using a novel {\it minimum spanning tree} based
    clustering method, \peace\/ is the equal of other leading tools in
    the literature in quality with an interface making it
    accessible to any user.  It produces results of quality virtually
    identical to those of the \wcd\/ tool when applied to Sanger
    sequences, significantly improved results over \wcd\/ when applied
    the products of Next Generation Sequencing Technology, and
    significantly improved results over \capthree\/ in both cases.  In
    short, \peace\/ provides an intuitive graphical user interface and
    a feature-rich, parallel clustering engine that proves to be a
    valuable addition to the leading cDNA clustering tools.}
